---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file  -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Blogdown website

A github/blogdown website with hugo

<!-- badges: start -->
![Render2README](https://github.com/norman-ds/website/workflows/Render2README/badge.svg)
<!-- badges: end -->

## DevOps

This project follows a continuous process approach covering software development and IT operations. All scripts are written in [R](https://www.r-project.org). The [Docker](https://hub.docker.com/r/rocker/verse) container system is used for reproducible software development. The versioning system is [GitHub](https://help.github.com/en/actions/building-and-testing-code-with-continuous-integration), GitHub *Action* for CI/CD and [Netlify](https://www.netlify.com) as Webserver.


The RStudio IDE is launched in a docker and accessed via the browser (http://localhost:8787).

```
docker run --name website -d -p 8787:8787 -v $(pwd):/home/rstudio -e PASSWORD=pwd rocker/verse:3.6.3
```

Next we need to install the blogdown package in R and the static site generator Hugo (https://gohugo.io) version *0.74.3*.

```
install.packages('blogdown')
blogdown::install_hugo(version="0.74.3")
```

To use the theme *data-science* from [Amber Thomas](https://github.com/ProQuestionAsker/websiteSource), you'll need to download all the files in that directory with *svn*, since *git* won't work for this target. Be careful with the hugo version, since it was written for an older version *0.54.0*.

```
svn export https://github.com/ProQuestionAsker/websiteSource/trunk/themes/data-science 

# the static files too
svn export https://github.com/ProQuestionAsker/websiteSource/trunk/static
```

The docker image of *rocker/verse* has the R version 3.6.3 and some packages installed and saves us from having to install them again.

```{R}
sessionInfo()
```

The following is a list of the few packages used (with version) ...

```{R}
libs <- c("blogdown")
ip <- installed.packages(fields = c("Package", "Version"))
ip <- as.data.frame(ip)
ip <- ip[ip[,c("Package")] %in% libs,]
paste(ip[,c("Package")],ip[,c("Version")])
```

... and the hugo version

```{r}
blogdown::hugo_version()
```


## Local Testing

Since Rstudio runs in a container a simple extra web server is used for testing static websites. To start from terminal a HTTPServer go to the directory *public* and type:

```
python -m SimpleHTTPServer 8000
```
